Title here \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2022-12-13 manuscript/manuscript.tex
1d model

% !TeX program = pdfLaTeX
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

@@

% structural markers
\def\div{\;|\;}
\def\bigdiv{\;\big|\;}
\def\Bigdiv{\;\Big|\;}
\def\Biggdiv{\;\Bigg|\;}

@@

Fig.~\ref{fig:tbd} shows the stable $V$ populations for differing values of $H$. 
Here one sees that as $H\to T_2$, the top stable state is annihilated with the unstable fixed point.
This way, if, e.g.\ $H$ were to slowly drift until $H=T_2$, the system would collapse to the low stable state, leading to a near extinction of $V$.

>>>>

% !TeX program = pdfLaTeX
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}

@@

% structural markers
\def\div{\;|\;}
\def\bigdiv{\;\big|\;}
\def\Bigdiv{\;\Big|\;}
\def\Biggdiv{\;\Bigg|\;}
\def\darg{\;\cdot\;}

% comments / colors
\definecolor{Fabulous}{RGB}{220,0,100}
\newcommand{\fm}[1]{{\color{Fabulous}\bf [FMM: #1]}}

@@

Fig.~\ref{fig:tbd} shows the stable $V$ populations for differing values of $H$. 
Here one sees that as $H\to T_2$, the top stable state is annihilated with the unstable fixed point.
A possible situation of concern here is the following:
The system begins in the high stable point for some $H<T_2$.
Slowly, $H$ slowly drifts upward, bringing the system up to $H=T_2$.
At this point, the system suddenly finds itself in the lower stable point's ‘‘basin’’---this leads to a quick collapse of $V$ down to the stable point.
Along a similar vein, if the system's evolution is noisy, then this catastrophe may happen for lower $H$ values: for $H$ close enough to $T_2$, there is a large probability that the $V$ crosses the unstable state and collapses towards the lower stable state.
\fm{Maybe this can be explained in the figure better?}

This way, if, e.g.\ the system is at the high stable state for low $H$, and $H$ were to slowly drift until $H=T_2$, the system would collapse to the low stable state, leading to a near extinction of $V$.

\hypertarget{paragraph-headings}{%
\paragraph{System~\eqref{eq:may77} as a simple fishery model.}\label{p:may as fishery}}
We reinterpret the model~\eqref{eq:may77} as a simplified model for a fishery.
There is some precedent for this already in~\cite{may77}, however our approach here is not in 1-to-1 correspondence to the approach used in that reference.
\fm{Refers to the fact that in the reference $F(\darg)$ is our harvest quota, using constant effort.
But here, it is a predation term, we compete with the predator in this case.}

% Ref.~\cite{may77} points out that the system presented above can be reinterpreted as a simple model for a fishery, where quotas are set using a constant effort rule.
% Here, the natural dynamics of $V$ is purely logistic growth, which is hampered by human harvesting according to the function $F$.
% This way, $H$ is the effort allowed for the sake of quotas.
% \footnote{%
%   The non-linearity of the $F$ function is justified in the fact that, for low very populations $V$, the effort necessary to obtain a constant-size catch grows faster than $H\sim 1/V$.
%   Here, for our case, $H\sim 1/V^2$ is used.
% }

We use this
